Solar wind prediction for the Solar Probe Plus orbit

### 2017-04-08 paperMVVB/sections/abstract.tex
removed some in-tex comments, table1 error fixed, table4 layout changed

\abstract
{In view of the planned near-Sun spacecraft mission Solar~Probe~Plus (SPP) the solar wind environment for its mission duration (2018--2025) and down to its intended closest perihelion (\num{9.86}~solar radii) is extrapolated using in situ data. This yet uncharted region is of special interest because the critical Alfvénic and sonic surfaces are believed to lie within and thus still part of the solar wind acceleration as well.}	%context
{We present an empirical solar wind model for the inner heliosphere which is derived from Helios and OMNI in situ data. The space probes Helios~1 and Helios~2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of \SIrange{0.29}{0.98}{\au}. The OMNI data set consists of multi-spacecraft intercalibrated in situ data from \SI{1}{\au}. This model is used together with sunspot number predictions to estimate the frequency distributions of major solar wind parameters SPP will encounter on its mission.}	%aims
{The model covers the solar wind's magnetic field strength and its plasma parameters proton density, velocity and temperature.
Their individual frequency distributions are represented with lognormal functions. In addition, we also consider the velocity distribution's bi-componental shape, consisting of a slower and a faster part. The model accounts for solar activity and for solar distance dependency by shifting of these lognormal distributions. We compile functional relations to solar activity by correlating and fitting the frequency distributions with the sunspot number (SSN), using almost five solar cycles of OMNI data. Further, based on the combined data set from both Helios probes, the parameters' frequency distributions are fitted over solar distance to obtain exponential dependencies. Combining both the solar cycle and the solar distance relations, we get a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic.}	%methods
{The inclusion of SSN predictions and the extrapolation to the SPP perihelion region enables us to estimate the solar wind environment at SPP's planned orbital positions during its mission time.}	%results
{}	%conclusions
%\SI{0.0459}{\au}

@@

%extrapolated ranges \SI{95.45}{\percent} of the solar wind parameter values lie within. The ranges are for the magnetic field strength \SIrange{522}{2725}{nT}, for the velocity \SIrange{209.4}{506}{\km\per\s}, for the density \SIrange[scientific-notation=fixed, fixed-exponent=3, range-units=brackets]{1.319e3}{1.72e4}{\per\cm\cubed} and for the temperature \SIrange[scientific-notation=fixed, fixed-exponent=6, range-units=brackets]{4.18e5}{1.59e7}{\K}.
%These ranges are consistent with... and differ with...

>>>>

\abstract
{In view of the planned near-Sun spacecraft mission Solar~Probe~Plus (SPP) the solar wind environment for its mission duration (2018--2025) and down to its intended closest perihelion (\num{9.86}~solar radii) is extrapolated using in situ data. This yet uncharted region is of special interest because the critical Alfvénic and sonic surfaces are believed to lie within and thus still part of the solar wind acceleration as well.}	%context
{We present an empirical solar wind model for the inner heliosphere which is derived from Helios and OMNI in situ data. The space probes Helios~1 and Helios~2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of \SIrange{0.29}{0.98}{\au}. The OMNI data set consists of multi-spacecraft intercalibrated in situ data from \SI{1}{\au}. This model is used together with sunspot number predictions to estimate the frequency distributions of major solar wind parameters SPP will encounter on its mission.}	%aims
{The model covers the solar wind's magnetic field strength and its plasma parameters proton density, velocity and temperature.
Their individual frequency distributions are represented with lognormal functions. In addition, we also consider the velocity distribution's bi-componental shape, consisting of a slower and a faster part. The model accounts for solar activity and for solar distance dependency by shifting of these lognormal distributions. We compile functional relations to solar activity by correlating and fitting the frequency distributions with the sunspot number (SSN), using almost five solar cycles of OMNI data. Further, based on the combined data set from both Helios probes, the parameters' frequency distributions are fitted over solar distance to obtain exponential dependencies. Combining both the solar cycle and the solar distance relations, we get a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic.}	%methods
{The inclusion of SSN predictions and the extrapolation to the SPP perihelion region enables us to estimate the solar wind environment at SPP's planned orbital positions during its mission time. The estimated solar wind values at SPP's nearest perihelion vary up to +-XX~\%, arising only from differing next solar cycle amplitude assumptions.}	%results
{}	%conclusions

@@

%\SI{0.0459}{\au}
%extrapolated ranges \SI{95.45}{\percent} of the solar wind parameter values lie within. The ranges are for the magnetic field strength \SIrange{522}{2725}{nT}, for the velocity \SIrange{209.4}{506}{\km\per\s}, for the density \SIrange[scientific-notation=fixed, fixed-exponent=3, range-units=brackets]{1.319e3}{1.72e4}{\per\cm\cubed} and for the temperature \SIrange[scientific-notation=fixed, fixed-exponent=6, range-units=brackets]{4.18e5}{1.59e7}{\K}.
%These ranges are consistent with... and differ with...

### 2017-04-08 paperMVVB/sections/content.tex
removed some in-tex comments, table1 error fixed, table4 layout changed

This general model is then fed with a SSN prediction and extrapolated to SPP's planned orbital positions.\\
% 
% \begin{itemize}
% % 	\item We determine the fit function type for the parameters' frequency distributions with OMNI data.
% %	\item We determine the fit function type for the parameters' solar cycle dependency with OMNI and SSN data.
% % 	\item We determine the fit function type for the parameters' distance dependency with Helios data.
% 	\item Time dependent (yearly) distribution magnitudes versus solar activity. for OMNI
% % 	\item The function's behavior in direction of Sun down to \SI{0.0459}{\au} is evaluated.
% % 	\item We fit exponential (double) lognormal functions to (distance-binned) Helios data (Helios solar wind model).
% % 	\item We combine the obtained distance dependencies with the obtained solar activity relations (dynamical solar wind model).
% 	\item resulting dynamical model dependencies (distance, SSN)
% 	\item use extrapolated SSN (SILSO) of SPP mission for solar wind extrapolation (SPP solar wind estimation model).
% \end{itemize}
%

%lognormal fitting
%%%%%%%%%%%%%%%%%%
\section{Frequency distributions}
\label{sec:frequency_distribution}
This section looks at the solar wind parameters' frequency distributions which we extract from the in situ OMNI data set. We determine adequate fit function types and evaluate how suitable they are to represent the frequencies' shapes.

@@

Next, we look for a suitable fit function for the resulting histogram shape of the solar wind parameters' frequency distributions.
% $B$: bin size 0.5~nT\\
% $v$: bin size 10~km/s\\
% $n$: bin size 1~cm$^{-3}$\\
% $T$: bin size 10\,000~K\\

@@

%choice of distribution function?/why lognormal function?

@@

			&\multicolumn{1}{c}{$W_2$}	&5.9089(53)	&3.72(20)	&	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\

@@

% fit data difference (normed area):\\
% B: 0.0682978\\
% v: 0.186874 -> 0.0419676 (double fit)\\
% n: 0.0648273\\
% T: 0.0578349\\

From visual inspection, the resulting curves match well with the shape of the magnetic field strength, density and temperature distributions (Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}). However, for the velocity the fit function seems insufficient in describing its more complex shape, especially at its peak position and the faster end of the distribution. Its sum of absolute residuals (SAR) between data and fit is almost three times larger than those from the other parameters (Table~\ref{tab:lognormal_fit_parameters}). They can be compared, because the area of probability density functions is unity.
\begin{figure*}
	\includegraphics[width=18cm]{figures/histogram_fits_4_a_zoom_paper_pdfplot.pdf}
	\caption{Frequency distributions of the four solar wind parameters and their lognormal fits. The histograms have bins of 0.5~nT, 10~km/s, 1~cm$^{-3}$ and 10\,000~K and are based on the hourly OMNI data set. The fit's median and mean values are indicated as well. The insets only have zoomed-in frequency axes, their x-axes stay the same.}
	\label{fig:histogram_fits_4_a_zoom_paper_pdfplot}
\end{figure*}
% From the normed stdfit values (Table~\ref{tab:single_lognormal_fit_parameters}) we see that the velocity fit is not that good... \\
% While by visual inspection it is obvious, but also fit stdfit is an indication for a bad fit...\\
% What we see at visual inspection is the area difference between the fit and the data. This area is for the velocity almost three times larger than the other's.\\

@@

yearly SSN sw model to sw data fits -> SSN dependency (figs)\\

\subsection{SSN fitting}
\label{sec:ssn_fitting}
To be able to shift the distributions with SSN, add fit a linear SSN dependency to the median
\begin{align}
	x_\text{med}(ssn) &= a_\text{med} \cdot ssn + b_\text{med}\,,	\label{eq:median_with_ssn}
\end{align}
using a factor to the SSN $a_\text{med}$ with a baseline $b_\text{med}$. We relate the mean with a scaling factor to the median to keep the new SSN dependency:
\begin{align}
	x_\text{avg}(ssn) &= (1 + a_\text{avg}) \cdot x_\text{med}(ssn)\,.	\label{eq:mean_with_ssn}
\end{align}
With the implementation of these relations into the lognormal function (\ref{eq:single_lognormal_fit_function}), the new dynamic fit function $W'(x,ssn)$ is then fitted to the yearly data. The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.\\
\begin{table*}
	\caption{Resulting fit coefficients from the data fitting with SSN. For the velocity the fit parameters from the double lognormal fit and their balancing function are given. The values in brackets are the estimated standard deviation of each fit parameter.}
	\label{tab:ssn_fit_parameters}
	\centering
%	\sisetup{table-figures-integer=1, table-figures-decimal=4, table-figures-exponent=1}
	\begin{tabular}{l@{} c@{}
		S[table-format = 1.3(2)e+1]
		S[table-format = 1.4(2)]
		S[table-format = 1.3(2)e+1]
		S[table-format = +1.3(2)e+1]
		c
		}
		\hline\hline
		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{2}{c}{Balance}\\
		\cline{3-4}\cline{6-7}
		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{SSN factor $a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{Baseline $b_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{Scaling factor $a_\text{avg}$}	&\multicolumn{1}{c}{SSN factor $c_a$}	&\multicolumn{1}{c}{Baseline $c_b$}\\
		\hline
		\multicolumn{2}{l}{Magnetic field}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--\\
%		\multicolumn{2}{l}{Velocity}	&2.514(93)e-3	&3.8521(90)	&2.392(26)e-2	&\multicolumn{1}{c}{--}	&--\\
		\multicolumn{2}{l}{Density}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--\\
		\multicolumn{2}{l}{Temperature}	&1.974(26)e-2	&5.729(19)	&6.541(28)e-1	&\multicolumn{1}{c}{--}	&--\\
		\hline
		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}\\
			&\multicolumn{1}{c}{$W_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{Values in their respective units \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
	}
\end{table*}

@@

For calculating the median and mean values at different solar distances the data is binned into \SI{0.01}{\au} bins, which is also the native precision in this data set.

@@

Naturally, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$. The additional fit parameters are the balancing parameter $c$ and from the second lognormal part $a_\text{med,2}$ and $a_\text{avg,2}$. The resulting fit coefficients for the four solar wind parameters are presented in Table~\ref{tab:extrapolation_model_fit_parameters}.
\begin{table*}
	\caption{These are the resulting fit coefficients with the single lognormal exponential function, respectively double lognormal for the velocity. The errors in brackets are the estimated standard deviations of each fit parameter.}
	\label{tab:extrapolation_model_fit_parameters}
	\centering
	\sisetup{table-figures-integer=1, table-figures-decimal=3, table-figures-exponent=0}
	\begin{tabular}{l c
	S[table-format = 1.3(2)]
	S[table-format = 1.3(2), table-space-text-post = a, table-align-text-post = false]
	S[table-format = 1.3(2), table-space-text-post = a, table-align-text-post = false]
	S[table-format = +1.4(2)]}
		\hline\hline
		\multicolumn{2}{l}{Parameter}	&$c$	&\multicolumn{1}{c}{$a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$a_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b$}\\
		\hline
		\multicolumn{2}{l}{Magnetic field}	&\multicolumn{1}{c}{--}	&5.358(25)	&5.705(28)	&-1.662(11)\\
		\multicolumn{2}{l}{Density}	&\multicolumn{1}{c}{--}	&5.424(33)	&6.845(47)	&-2.114(20)\\
		\multicolumn{2}{l}{Temperature}	&\multicolumn{1}{c}{--}	&6.357(64)	&10.72(14)	&-1.100(20)\\
		\hline
		\multirow{1}{*}{Velocity}	&$W''_1$	&\multirow{2}{*}{0.557(45)}	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}\\
			&$W''_2$	&	&5.26(13)	&5.42(11)	&\\
		\cline{2-6}
		\multicolumn{2}{r}{$W''_\text{II}$}	&\multicolumn{1}{c}{--}	&4.35(13)\tablefootmark{b}	&4.77(11)\tablefootmark{b}	&\multicolumn{1}{c}{--}\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{Values in their respective units \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
		\tablefoottext{b}{Velocity median and mean \SI{1}{\au} values for the resulting function. Error estimates derived from the individual fit part errors.}
	}
\end{table*}

@@

%SSN prediction
choosing SSN prediction source as input (SIDC + SWPC + previous cycle), (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_b_plot})\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_b_plot.pdf}}
	\caption{SPP's solar distance during its mission time (top). Consecutive Venus flybys bring its perihelia nearer to the Sun. Actual and predicted SSN (bottom), i.e. SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and simply shifted SSN from previous cycle~24, together with two alternative trends of half and twice the amplitude.}
	\label{fig:SPP_orbit_predicted_SSN_overview_b_plot}
\end{figure}

>>>>

This general model is then fed with a SSN prediction and extrapolated to SPP's planned orbital positions.\\

%lognormal fitting
\section{Frequency distributions}
\label{sec:frequency_distribution}

This section looks at the solar wind parameters' frequency distributions which we extract from the in situ OMNI data set. We determine adequate fit function types and evaluate how suitable they are to represent the frequencies' shapes.

@@

Next, we look for a suitable fit function for the resulting histogram shape of the solar wind parameters' frequency distributions.

@@

%choice of distribution function---why lognormal function?

@@

			&\multicolumn{1}{c}{$W_2$}	&3.68(20)	&3.72(20)	&	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\

@@

% fit data difference (normed area):\\
% B: 0.0682978\\
% v: 0.186874 -> 0.0419676 (double fit)\\
% n: 0.0648273\\
% T: 0.0578349\\

From visual inspection, the resulting curves match well with the shape of the magnetic field strength, density and temperature distributions (Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}). However, for the velocity the fit function seems insufficient in describing its more complex shape, especially at its peak position and the faster end of the distribution. Its sum of absolute residuals (SAR) between data and fit is almost three times larger than those from the other parameters (Table~\ref{tab:lognormal_fit_parameters}). They can be compared, because the area of probability density functions is unity.
\begin{figure*}
	\includegraphics[width=18cm]{figures/histogram_fits_4_a_zoom_paper_pdfplot.pdf}
	\caption{Frequency distributions of the four solar wind parameters and their lognormal fits. The histograms have bins of 0.5~nT, 10~km/s, 1~cm$^{-3}$ and 10\,000~K and are based on the hourly OMNI data set. The fit's median and mean values are indicated as well. The insets only have zoomed-in frequency axes, their x-axes stay the same.}
	\label{fig:histogram_fits_4_a_zoom_paper_pdfplot}
\end{figure*}

@@

yearly SSN sw model to sw data fits -> SSN dependency (new figs)\\

\subsection{SSN fitting}
\label{sec:ssn_fitting}
To be able to shift the distributions with SSN, add fit a linear SSN dependency to the median
\begin{align}
	x_\text{med}(ssn) &= a_\text{med} \cdot ssn + b_\text{med}\,,	\label{eq:median_with_ssn}
\end{align}
using a factor to the SSN $a_\text{med}$ with a baseline $b_\text{med}$. We relate the mean with a scaling factor to the median to keep the new SSN dependency:
\begin{align}
	x_\text{avg}(ssn) &= (1 + a_\text{avg}) \cdot x_\text{med}(ssn)\,.	\label{eq:mean_with_ssn}
\end{align}
With the implementation of these relations into the lognormal function (\ref{eq:single_lognormal_fit_function}), the new dynamic fit function $W'(x,ssn)$ is then fitted to the yearly data. The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.\\
\begin{table*}
	\caption{Resulting fit coefficients from the data fitting with SSN. For the velocity the fit parameters from the double lognormal fit and their balancing function are given. The values in brackets are the estimated standard deviation of each fit parameter.}
	\label{tab:ssn_fit_parameters}
	\centering
	\begin{tabular}{l@{} c@{}
		S[table-format = 1.3(2)e+1]
		S[table-format = 1.4(2)]
		S[table-format = 1.3(2)e+1]
		S[table-format = +1.3(2)e+1]
		c
		}
		\hline\hline
		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{2}{c}{Balance}\\
		\cline{3-4}\cline{6-7}
		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{SSN factor $a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{Baseline $b_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{Scaling factor $a_\text{avg}$}	&\multicolumn{1}{c}{SSN factor $c_a$}	&\multicolumn{1}{c}{Baseline $c_b$}\\
		\hline
		\multicolumn{2}{l}{Magnetic field}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--\\
%		\multicolumn{2}{l}{Velocity}	&2.514(93)e-3	&3.8521(90)	&2.392(26)e-2	&\multicolumn{1}{c}{--}	&--\\
		\multicolumn{2}{l}{Density}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--\\
		\multicolumn{2}{l}{Temperature}	&1.974(26)e-2	&5.729(19)	&6.541(28)e-1	&\multicolumn{1}{c}{--}	&--\\
		\hline
		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}\\
			&\multicolumn{1}{c}{$W_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{Values in their respective units \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
	}
\end{table*}

@@

For calculating the median and mean values at different solar distances the data is binned into \SI{0.01}{\au} bins, which is also the native precision in this data set.\\

@@

Naturally, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$. The additional fit parameters are the balancing parameter $c$ and from the second lognormal part $a_\text{med,2}$ and $a_\text{avg,2}$. The resulting fit coefficients for the four solar wind parameters are presented in Table~\ref{tab:extrapolation_model_fit_parameters}.
\begin{table*}
	\caption{These are the resulting fit coefficients with the single lognormal exponential function, respectively double lognormal for the velocity. The errors in brackets are the estimated standard deviations of each fit parameter.}
	\label{tab:extrapolation_model_fit_parameters}
	\centering
	\sisetup{table-figures-integer=1, table-figures-decimal=3, table-figures-exponent=0}
	\begin{tabular}{l c
	S[table-format = 1.3(2), table-space-text-post = a, table-align-text-post = false]
	S[table-format = 1.3(2), table-space-text-post = a, table-align-text-post = false]
	S[table-format = +1.4(2)]
	S[table-format = 1.3(2)]}
		\hline\hline
		\multicolumn{2}{l}{Parameter}	&\multicolumn{1}{c}{$a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$a_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b$}	&$c$\\
		\hline
		\multicolumn{2}{l}{Magnetic field}	&5.358(25)	&5.705(28)	&-1.662(11)	&\multicolumn{1}{c}{--}\\
		\multicolumn{2}{l}{Density}	&5.424(33)	&6.845(47)	&-2.114(20)	&\multicolumn{1}{c}{--}\\
		\multicolumn{2}{l}{Temperature}	&6.357(64)	&10.72(14)	&-1.100(20)	&\multicolumn{1}{c}{--}\\
		\hline
		\multirow{1}{*}{Velocity}	&$W''_1$	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}	&\multirow{2}{*}{0.557(45)}\\
			&$W''_2$	&5.26(13)	&5.42(11)	&	&\\
		\cline{2-6}
		\multicolumn{2}{r}{$W''_\text{II}$}	&4.35(13)\tablefootmark{b}	&4.77(11)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{Values in their respective units \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
		\tablefoottext{b}{Velocity median and mean \SI{1}{\au} values for the resulting function. Error estimates derived from the individual fit part errors.}
	}
\end{table*}

@@

%SSN prediction
choosing SSN prediction sources as input:\\
SIDC prediction---12-month forecast (Kalman fiter combined method)\\
The SWPC prediction (until end of current cycle/end of 2019) follows a consensus of the Solar~Cycle~24 Prediction~Panel.\\
For the prediction of the next solar cycle we simply assume a course similar to the last and thus we simply shift the last cycle by 11~years. Additionally we consider the two alternatives of half and twice the amplitude.\\
SIDC + SWPC + previous cycle~24 (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_b_plot})\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_b_plot.pdf}}
	\caption{SPP's solar distance during its mission time (top). Consecutive Venus flybys bring its perihelia nearer to the Sun. Actual and predicted SSN (bottom), i.e. SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and simply shifted SSN from previous cycle~24, together with two alternative trends of half and twice the amplitude.}
	\label{fig:SPP_orbit_predicted_SSN_overview_b_plot}
\end{figure}
